The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-09 src/paper/report.tex

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
at least one day to be processed and there are aggregate capacity constraints. In
contrast, rapid antigen tests yield immediate results. Specificity and sensitivity of
these tests is set according to data analyzed in \cite{Bruemmer2021, Smith2021,
Toptan2020}; sensitivity depends on the timing of the test relative to the onset of
infectiousness. After a phase-in period, all tests that are demanded will be performed.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require staff and students to be tested regularly. Rapid tests may be offered by
employers to on-site workers. Individuals may demand tests for private reasons, which
include having plans to meet other people, showing symptoms of CoViD-19, and a household
member having tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid
tests.\footnote{Positive test results or symptoms lead most individuals to reduce their
contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model_description}.}

@@

Our analysis has shown that during the transition to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A week of the fairly strict lockdown in early 2021 is
estimated to have cost around 20-30~Euros per capita \citep{Wollmershauser2021}; retail
prices for rapid tests were below one Euro in early June 2021 and below five Euros for
firms. While we do not distinguish between self-administered rapid tests and point of
care rapid tests, the former are likely to play a larger role for indication-driven
testing. Widespread availability at low prices seems important. However, they rely on
purely voluntary participation in a non-public setting. The benefit of point-of-care
rapid tests as a precondition to participate in leisure activities as well as mandatory
tests at the workplace or at school come from screening the entire population. This is
important because disadvantaged groups are less likely to be reached by testing campaigns
relying on voluntary participation \citep[e.g.][]{StillmanTonin2021}; at the same time,
these groups have a higher risk to contract CoViD-19 \citep{KochInstitut2021a}. Mandatory
tests at school and at the workplace will extend more into these groups. The same goes
for individuals who exhibit a low level of compliance with CoViD-19-related regulations.
Compared to vaccinations, rapid testing programmes allow a much quicker roll-out, making
it arguably the most effective tool to contain the pandemic in the short run.

>>>>

We include two types of tests. Polymerase chain reaction (PCR) tests reveal
whether an individual is infected or not; there is no uncertainty to the result.
PCR tests require at least one day to be processed and there are aggregate
capacity constraints. In contrast, rapid antigen tests yield immediate results.
Specificity and sensitivity of these tests is set according to data analyzed in
\cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test
relative to the onset of infectiousness  (we show our results are robust to more
conservative assumptions in
Section~\ref{subsec:robustness_rapid_test_sensitivity}). After a phase-in
period, all tests that are demanded will be performed.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand.
Schools may require staff and students to be tested regularly. Rapid tests may
be offered by employers to on-site workers. Individuals may demand tests for
private reasons, which include having plans to meet other people, showing
symptoms of CoViD-19, and a household member having tested positively for the
virus. We endow each agent with an individual compliance parameter. This
parameter determines whether she takes up rapid tests.\footnote{Positive test
    results or symptoms lead most individuals to reduce their contacts; this is why
    tests impact the actual contacts in Figure~\ref{fig:model_description}.}

@@

Our analysis has shown that during the transition to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A week of the fairly strict lockdown in early 2021 is
estimated to have cost around 50~Euros per capita \citep{Wollmershauser2021}; retail
prices for rapid tests were below one Euro in early June 2021 and below five Euros for
firms. While we do not distinguish between self-administered rapid tests and point of
care rapid tests, the former are likely to play a larger role for indication-driven
testing. Widespread availability at low prices seems important. However, they rely on
purely voluntary participation in a non-public setting. The benefit of point-of-care
rapid tests as a precondition to participate in leisure activities as well as mandatory
tests at the workplace or at school come from screening the entire population. This is
important because disadvantaged groups are less likely to be reached by testing campaigns
relying on voluntary participation \citep[e.g.][]{StillmanTonin2021}; at the same time,
these groups have a higher risk to contract CoViD-19 \citep{KochInstitut2021a}. Mandatory
tests at school and at the workplace will extend more into these groups. The same goes
for individuals who exhibit a low level of compliance with CoViD-19-related regulations.
Compared to vaccinations, rapid testing programmes allow a much quicker roll-out, making
it arguably the most effective tool to contain the pandemic in the short run.
